Towards a classification framework for social machines

### 2013-02-24 latex/paper_new.tex
working on 4.3

@@

The four clusters of constructs generated by the process described in Section~\ref{meth}
are shown in full in Table \ref{table:constructs}, and are detailed below.

\begin{table}[htb]
\begin{center}
\begin{tabular}{|p{8cm}|}
\hline
{\bf Tasks} \\
\hline
Variety of types of contributions \\
Domain specificity \\
Participation is done to `get something done' \\
Participation is done `for fun' \\
Participation is done to exchange knowledge \\
Participation is done to be social \\
Participants are intrinsically motivated \\
Participants are motivated by extrinsic reward \\
\hline
{\bf Users and Roles} \\
\hline
Generality of Audience \\
Participant autonomy \\
Participant anonymity \\
Extent of hierarchical organisation of roles \\
Clear separation of roles/responsibilities among participants \\
\hline
{\bf Participation} \\
\hline
Participants' (geographic) location is used by the service \\
Participation is done via: \\
\hspace{1cm} mobile devices \\
\hspace{1cm} web browsers \\
\hspace{1cm} apps \\
\hspace{1cm} sensors/sensing (location sensing and wearable devices) \\
Participation is done in a mobile context \\
\hline
{\bf Computation, Output and Benefit} \\
\hline
Output solves a computational problem \\
Output requires human insight \\
Output is a subjective appraisal \\
Participants directly benefit from participating \\
Service/Platform derives benefit from participant participation \\
Participants'' friends/social network benefit from participation \\
Participation is for the benefit of a specific person/group other than the participant or platform owner \\
Participation is for the benefit of society/the world at large  \\
\hline
\end{tabular}
\end{center}
\caption{Consolidated constructs of social machines.} \label{table:constructs}
\end{table}

\subsubsection{Tasks}

@@

{\bf The roles of the participants and the social network they form}

\subsubsection{Participation (How users interact with the Social Machine)}

\subsubsection{Computation, Output and Benefit}

>>>>

%% Constructs =============================================================

@@

The clustering process described in Section~\ref{meth} yielded both a
reduction in the overall number of constructs (in particular an
elimination of overrepresented areas) but also identificaiton of four
simple themes: sets of constructs pertaining to users and roles within
each machine, second, the nature of tasks, problems and activities
performed through and using the machine, third, motivation for
participation, finally, the contexts of participation.  Each of these
clusters contain 5-8 constructs as illustrated in Table
\ref{table:constructs}; we describe each of these themes in the
following subsections.

\begin{table}[htb]
\begin{center}
\begin{tabular}{|p{8cm}|}
\hline
{\bf Users and Roles} \\
\hline
Generality of Audience \\
Participant autonomy \\
Participant anonymity \\
Extent of hierarchical organisation of roles \\
Clear separation of roles/responsibilities among participants \\
\hline
{\bf Tasks} \\
\hline
Task involves subjective appraisal of content \\
Task solves (a defnable) computation problem/set of problems\\
Domain-specificity of tasks \\
Service/platform derives benefit from participation \\
Variation in types of contributions and tasks \\
{\bf Motivation} \\
Participants are intrinsically motivated:\\
\hspace{1cm} to gain/share knowledge \\
\hspace{1cm} to ``get something done'' \\
\hspace{1cm} to ``for fun/entertainment''\\
\hspace{1cm} to ``be social'' \\
Participation is motivated by extrinsic reward (payment, status etc) \\
Participation is done for the benefit of a specific third-party \\
Participation is done for the benefit of society as a whole \\
\hline
{\bf Context of Participation} \\
\hline
Participants' (geographic) location is relevant to the service \\
Participation is done via: \\
\hspace{1cm} mobile devices \\
\hspace{1cm} web browsers \\
\hspace{1cm} apps \\
\hspace{1cm} sensors/sensing (location sensing and wearable devices) \\
Participation is done in a mobile context \\
\hline
\end{tabular}
\end{center}
\caption{Consolidated constructs of social machines.} \label{table:constructs}
\end{table}

\subsubsection{Users and Roles}
The first set of constructs pertain to the human participants of
social machines and the way(s) participants are organised within them.
First, whether participants consistute members of the general public,
or are of a specific demongraphic, external group or organisation,
occupation, or of a particular expertise.  Second, pertain to how
constrained interaction is among members of the machine (lack of
\emph{autonomy}), and the degree to which participants are anonymous.

\subsubsection{Tasks, Problems and Activiites}}

The first set of constructs pertain to \emph{what} human components
of the social machine do within the system.  These constructs pertain
to the

@@

% {\bf The roles of the participants and the social network they form}

% \subsubsection{Participation (How users interact with the Social Machine)}

\subsubsection{Participation - \emph{How and when user participate}}

\subsubsection{Problems Solved and Benefit Derived}
